Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-21 cordillera-cycle.tex
Rev. Jarosch: add new figures and tables.

@@

@@

@@

@@

>>>>

\clearpage{}  % new page for tables

@@

\begin{table*}
\caption{%
      Parameter values used in the sensitivity test.}
\label{tab:sens_params}
%\centering\makebox[\textwidth]
{\begin{tabular}{l|ccccc|cc|cc}
    \tophline
            & \multicolumn{5}{c|}{Rheology}
            & \multicolumn{2}{c|}{Sliding}
            & \multicolumn{2}{c}{GRIP scaling} \\
    Config. & $A_c$ & $A_w$ & $Q_c$ & $Q_w$ & $E_{SIA}$
            & $\delta$ & $W_{max}$ & $f$ & $T_{[32, 22]}$ \\
            & \multicolumn{2}{c}{(\unit{Pa^{-3}\,s^{-1}})}
            & \multicolumn{2}{c}{(\unit{J\,mol^{-1}})}
            & & & (m) \\
    \middlehline
    Default$^1$  & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.02 & 2 & 0.38 & 6.2 \\
    \cline{1-10}
    Soft ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 5 & 0.02 & 2 & 0.40 & 6.6 \\
    Hard ice$^2$ & $2.847\times 10^{-13}$
                 & $2.356\times 10^{-2}$
                 & $   60\times 10^3$
                 & $  115\times 10^3$
                 & 1 & 0.02 & 2 & 0.37 & 6.0 \\
    \cline{1-10}
    Soft bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.01 & 1 & 0.40 & 6.5 \\
    Hard bed     & $ 3.61\times 10^{-13}$
                 & $ 1.73\times 10^3$
                 & $   60\times 10^3$
                 & $  139\times 10^3$
                 & 1 & 0.05 & 5 & 0.36 & 5.9 \\
    \bottomhline
\end{tabular}}
\belowtable{%
      After $^1$\citet{Paterson.Budd.1982,Bueler.Pelt.2015};
      and $^2$\citet{Cuffey.Paterson.2010}.}
\end{table*}

\clearpage{}  % avoid three tables on one page

@@

\begin{table*}[p]
\caption{%
      Extremes in Cordilleran ice sheet volume and extent corresponding to
      MIS~4, 3 and 2 using the GRIP paleo-climate forcing with each
      parameter configuration (Fig.~3). Relative differences (R. diff.) give
      rough error estimates related to varying selected ice rheology and
      basal sliding parameters (Table~\ref{tab:sens_params}).}
\label{tab:sens_extrema}
%\centering\makebox[\textwidth]
{\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Config.  &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    Default  &  57.59 &  42.91 &  19.14
             &   1.93 &   0.67 &   2.09
             &   7.43 &   1.54 &   8.62 \\
    \cline{1-10}
    Soft ice &  58.89 &  49.97 &  21.57
             &   1.96 &   0.54 &   2.08
             &   6.58 &   1.03 &   6.88 \\
    Hard ice &  57.32 &  42.90 &  19.14
             &   1.90 &   0.75 &   2.12
             &   7.83 &   1.91 &   9.46 \\
    R. diff. &    3\% &   16\% &   13\%
             &    3\% &   31\% &    2\%
             &   17\% &   57\% &   30\% \\
    \cline{1-10}
    Soft bed &  58.90 &  49.21 &  19.53
             &   1.88 &   0.55 &   2.05
             &   6.46 &   1.03 &   7.52 \\
    Hard bed &  57.31 &  42.91 &  19.14
             &   1.93 &   0.96 &   2.13
             &   7.99 &   2.89 &   9.31 \\
    R. diff. &    3\% &   15\% &    2\%
             &    3\% &   62\% &    4\%
             &   21\% &  120\% &   21\% \\
    \bottomhline
\end{tabular}}
\end{table*}

\clearpage{}  % new page for figures and avoid too many unprocessed floats

@@

\begin{figure}%
\includegraphics{sens_plot_rheo}
\caption{%
      Ice softness parameter, $A$, as a function of pressure-adjusted
      temperature, $T_{pa}$, for the default \citep{Paterson.Budd.1982},
      hard ice \citep[with $E_{SIA}=1$]{Cuffey.Paterson.2010}, and soft ice
      \citep[with $E_{SIA}=5$]{Cuffey.Paterson.2010} rheologies, using a
      linear scale (top panel) and logarithmic scale (bottom panel). Figure
      made using Eqn.~\ref{eqn:softness} with parameters from
      Table~\ref{tab:sens_params}.}
\label{fig:sens_plot_rheo}%
\end{figure}%

\begin{figure}%
\includegraphics{sens_plot_ntil}
\caption{%
      Effective pressure, $N$, as a function of water content in the till,
      $W$, for the default ($\delta=0.02$, $W_{max}=2$\,m), hard bed
      ($\delta=0.05$, $W_{max}=5$\,m), and soft bed ($\delta=0.01$,
      $W_{max}=1$\,m) sliding parametrisations, using a linear scale (top
      panel) and a logarithmic scale (bottom panel). Calculations are made
      for an ice thickness, $h$, of 1000\,m. Figure made using
      Eqn.~\ref{eqn:ntil} with parameters from Table~\ref{tab:sens_params}
      after \citet[Fig.~1]{Bueler.Pelt.2015}.}
\label{fig:sens_plot_ntil}%
\end{figure}%

@@

\begin{figure*}
\includegraphics{sens_ts}
\caption{%
      Modelled sea-level relevant ice volume through the last 120\,ka in the
      simulation forced by the GRIP paleo-climate record, using default
      parameters (black curves), different ice rheology parameters (top
      panel), and different basal sliding parameters (bottom panel). Gray
      fields indicate Marine Oxygen Isotope Stage (MIS) boundaries for MIS~2
      and MIS~4 according to a global compilation of benthic
      \chem{\delta^{18}O} records \citep{Lisiecki.Raymo.2005}.}
\label{fig:sens_ts}
\end{figure*}
